---
## Plot of the data
```{r, echo = FALSE, fig.height=5,fig.width=5}
library(UsingR)
data(diamond)
library(ggplot2)
g = ggplot(diamond, aes(x = carat, y = price))
g = g + xlab("Mass (carats)")
g = g + ylab("Price (SIN $)")
g = g + geom_point(size = 7, colour = "black", alpha=0.5)
g = g + geom_point(size = 5, colour = "blue", alpha=0.2)
g = g + geom_smooth(method = "lm", colour = "black")
g
```

---
## Fitting the linear regression model
```{r}
fit <- lm(price ~ carat, data = diamond)
coef(fit)
```

* We estimate an expected `r round(coef(fit)[2], 2)` (SIN) dollar increase in price for every carat increase in mass of diamond.
* The intercept `r round(coef(fit)[1], 2)` is the expected price
  of a 0 carat diamond.

---
## Getting a more interpretable intercept
```{r, echo = TRUE}
fit2 <- lm(price ~ I(carat - mean(carat)), data = diamond)
coef(fit2)
```

Thus $`r round(coef(fit2)[1], 1)` is the expected price for 
the average sized diamond of the data (`r mean(diamond$carat)` carats).

---
## Changing scale
* A one carat increase in a diamond is pretty big, what about
  changing units to 1/10th of a carat? 
* We can just do this by just dividing the coeficient by 10.
  * We expect  a `r round(coef(fit)[2], 2) / 10` (SIN) dollar   change in price for every 1/10th of a carat increase in mass of diamond.
* Showing that it's the same if we rescale the Xs and refit
```{r, echo = TRUE}
fit3 <- lm(price ~ I(carat * 10), data = diamond)
coef(fit3)
```

---
## Predicting the price of a diamond
```{r, echo = TRUE}
newx <- c(0.16, 0.27, 0.34, 0.5)
coef(fit)[1] + coef(fit)[2] * newx
predict(fit, newdata = data.frame(carat = newx))






data("cars")
cars.lm <- lm(dist ~ speed, data = cars)
summary(cars.lm)

new.dat <- data.frame(speed=30)
predict(cars.lm, newdata = new.dat, interval = 'confidence')


y <- t$revenue; x <- t$mcf; n <- length(y)
fit <- lm(dist ~ speed, data = cars)
e <- resid(fit)
yhat <- predict(fit)
max(abs(e -(y - yhat)))
max(abs(e - (y - coef(fit)[1] - coef(fit)[2] * x)))

x = coef(fit)[1] + coef(fit)[2] * c(30)
x

```
