---
title: "Using Volume as Revenue Predictor App"
subtitle: "Does it make sense to increase volume?, 08/20/2018"
author: "Jarvis Fosdick"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
all2017Data <- read.csv("RevVolume.csv", na.strings=c("-"))
cn <- c("isRegion", "area", "revenue", "mcf", "bbls", "date")
colnames(all2017Data) = cn
all2017Data$revenue <- as.numeric(gsub('[$,]', '', all2017Data$revenue))
all2017Data$mcf <- as.numeric(gsub('[$,]', '', all2017Data$mcf))
all2017Data$bbls <- as.numeric(gsub('[$,]', '', all2017Data$bbls))
all2017Data$area <- gsub('\\s+', '', all2017Data$area)

```

## Often we think more is better

Management always wants more as they believe the bottom line is increased volume!

### Using this shiny app Managers can:

- See if their area is trending upward with volume
- Predict their revenue
- Visualize trends by each area

## Consider this chart
```{r}
tt<- all2017Data[all2017Data$area == "SoutheastNewMexicoSEC",]
g = ggplot(tt, aes(x = mcf, y = revenue, colour = area))
g = g + xlab("Wellhead MCF per Day")
g = g + ylab("Revenue")
g = g + geom_smooth(method = "lm", colour = "black")
#g = g + geom_point(size = 1, colour = "black", alpha=0.5)
g = g + geom_point(size = 2, alpha=0.9)
g
```

### INCREASED VOLUME LOWERS PROFIT!


## Use The App to Find the Warning Signs

```{r fig.width=8,echo=FALSE}
library(png)
library(grid)
img <- readPNG("app.png")
 grid.raster(img)
```

## Our App Makes the Difference!
```{r}
tt<- all2017Data[all2017Data$area == "DJBasinSEC",]
g = ggplot(tt, aes(x = mcf, y = revenue, colour = area))
g = g + xlab("Wellhead MCF per Day")
g = g + ylab("Revenue")
g = g + geom_smooth(method = "lm", colour = "black")
#g = g + geom_point(size = 1, colour = "black", alpha=0.5)
g = g + geom_point(size = 2, alpha=0.9)
g
```

### Keep things going in the right direction!